---
title: "Building a prediction model on house prices"
author: Chiara Castelli
output: github_document
---

Define libraries and options for the cleaning process
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# packages <- c("readr", "tidyverse", "tidyr", "stringr", "stargazer", "Hmisc", "DescTools", "ggplot2", 'extrafont', 'ggpubr', 'janitor','forecast','ggcorrplot',               'fastDummies')

# Install packages if not already installed
# for (package in packages) {
#   if (!require(package, character.only = TRUE)) {
#     install.packages(package)
#     library(package, character.only = TRUE)
#   }
# }

library(readr)
library(tidyverse)
library(stringr)
library(tidyr)
library(stargazer)
library(Hmisc)
library(DescTools)
library(ggplot2)
library(extrafont)
library(ggpubr)
library(janitor)
library(forcats)
library(ggcorrplot)
library(fastDummies)

options(digits = 3)

```

Define folders and source functions
```{r include = FALSE, message = FALSE , warning = FALSE}

setwd("C:/Users/Castelli/Desktop/WU_exams/CEU_WiSe25/Machine_Learning/Assignment2/")

source("C:/Users/Castelli/DataAnalysis3/da_case_studies/ch00-tech-prep/theme_bg.R")
source("C:/Users/Castelli/DataAnalysis3/da_case_studies/ch00-tech-prep/da_helper_functions.R")


```

# Reading the Database 

```{r include = FALSE, message = FALSE , warning = FALSE}
# read db
MIQ1_db <- read_csv("C:/Users/Castelli/Desktop/WU_exams/CEU_WiSe25/Machine_Learning/Assignment2/MilanQ1listings/listings.csv",na = c("N/A", "NA") )

names(MIQ1_db)
length(unique(MIQ1_db$id)) # unique ID for each observation

```

```{r message = FALSE , warning = FALSE}
# drop some columns 
# not meaningful ones: e.g. scraping ids, url, descriptions, some host information etc.
MIQ1_db <- MIQ1_db[!(names(MIQ1_db) %in% c('listing_url', 'scrape_id', 'source', 'description','neighborhood_overview',"host_name","host_location", 'picture_url','host_url', 'host_about','host_thumbnail_url', 'has_availability', 'host_picture_url','host_listings_count','host_total_listings_count','host_has_profile_pic', 'latitude','longitude', 'calendar_updated','calendar_last_scraped') ) ]
MIQ1_db <- MIQ1_db[!(names(MIQ1_db) %like% c('calculated_host_listings%') ) ]

#sort(unique(MIQ1_db$last_scraped)) # date of scrapes is 24/03,25/03 and 05/04

# delete additional cols - this time quickly done by column index
MIQ1_db <- MIQ1_db[,-c(2,11, 12, 27:32, 38:40, 49:50)]
names(MIQ1_db)
```
According to this list, we can define 3 main variable groups:
- Host information
- Property characteristics : location and specific features
- Reservation: availability and review

# 1 Data Cleaning

In this section we work on the cleaning and editing of some variables/ group of variables.

## 1.1 Price (dependent variable)

``` {r include = T, message = FALSE , warning = FALSE}

# which(is.na(MIQ1_db$price))
# unique(MIQ1_db$price) # some empty strings - NA

MIQ1_db$price_n <- substr(MIQ1_db$price, 2,nchar(MIQ1_db$price))
MIQ1_db$price_n <- gsub(",", "", MIQ1_db$price_n)
MIQ1_db$price_n <- as.numeric(MIQ1_db$price_n)
unique(MIQ1_db$price[is.na(MIQ1_db$price_n)])

print('Nr missing prices')
NROW(which(is.na(MIQ1_db$price_n))) 
```

Drop missing prices

``` {r include = T, message = FALSE , warning = FALSE}
MIQ1_db <- MIQ1_db[!(is.na(MIQ1_db$price_n)),]
```

and compute the log scale for comparison (later)
``` {r include = T, message = FALSE , warning = FALSE}
# compute log for comparison
MIQ1_db$price_ln <- log(MIQ1_db$price_n)
```


## 1.2 Host information
```{r include = F, message = FALSE , warning = FALSE}

print("Nr. properties per host")
dim(MIQ1_db)[1]/length(unique(MIQ1_db$host_id)) # accom. /host
# some have multiple properties

head(MIQ1_db)
# change host rates into numeric

MIQ1_db$host_acceptance_rate <- gsub('%','', MIQ1_db$host_acceptance_rate )
MIQ1_db$host_acceptance_rate <- as.numeric(MIQ1_db$host_acceptance_rate)

MIQ1_db$host_response_rate <- gsub('%','', MIQ1_db$host_response_rate )
MIQ1_db$host_response_rate <- as.numeric(MIQ1_db$host_response_rate)

cols <- which(names(MIQ1_db) == "host_response_time"):which(names(MIQ1_db) == "host_is_superhost")

print("NAs by variable")
for (col in cols) {
  
  na_nr = sum(is.na(MIQ1_db[[col]]) )
  
  if (sum(is.na(MIQ1_db[[col]])) > 0) {
  
    print(names(MIQ1_db)[col])
    print(na_nr)
    
  }
}

# Deal with Missings 

# first check corr with dep variable
cor(MIQ1_db$price_n, MIQ1_db$host_acceptance_rate, use = 'complete.obs')
cor(MIQ1_db$price_n, MIQ1_db$host_response_rate, use = 'complete.obs')

# keep response rate ( higher corr). replace with median
MIQ1_db$d_miss_resp_rate <- 0
MIQ1_db$d_miss_resp_rate[is.na(MIQ1_db$host_response_rate)] <- 1
value_resp_rate = median(MIQ1_db$host_response_rate, na.rm = T)
MIQ1_db$host_response_rate[is.na(MIQ1_db$host_response_rate)] <- value_resp_rate

# replace categorical host_response_time & host_is_superhost with mode
table(MIQ1_db$host_response_time) # mode: within an hour 

MIQ1_db$d_miss_resp_time <- 0
MIQ1_db$d_miss_resp_time[is.na(MIQ1_db$host_response_time)] <- 1
MIQ1_db$host_response_time[is.na(MIQ1_db$host_response_time)] <- 'within an hour'

# create numerical variable host_resptime_n
MIQ1_db$host_resptime_n <- NA
MIQ1_db$host_resptime_n[MIQ1_db$host_response_time == "within an hour"]<- 1
MIQ1_db$host_resptime_n[MIQ1_db$host_response_time == "within a few hours"]<- 2
MIQ1_db$host_resptime_n[MIQ1_db$host_response_time == "within a day" ]<- 3
MIQ1_db$host_resptime_n[MIQ1_db$host_response_time == "a few days or more"]<- 4
summary(MIQ1_db$host_resptime_n)

# superhost - recode
table(MIQ1_db$host_is_superhost) # FALSE

MIQ1_db$d_miss_superhost <- 0
MIQ1_db$d_miss_superhost[is.na(MIQ1_db$d_miss_superhost)] <- 1
MIQ1_db$host_is_superhost[is.na(MIQ1_db$host_is_superhost)] <- 'FALSE'


```

## 1.3 Property 
### Location (Neighborhood) 

```{r include = F, message = FALSE , warning = FALSE}

# first, keep only BnBs within the city boundaries
# cols: "neighbourhood" "neighbourhood_cleansed" "neighbourhood_group_cleansed"   
which(is.na(MIQ1_db$neighbourhood_cleansed)) # start from this column 
unique(MIQ1_db$neighbourhood_cleansed[is.na(MIQ1_db$neighbourhood) | 
                                        !(MIQ1_db$neighbourhood %like% 'Milan%')])
# all names returned are Milanese neighbourhoods, keep all rows and  
# drop places lying outside the metro-line system (by vars: neighbourhood and neighbourhood_group_cleansed)

unique(MIQ1_db$neighbourhood)
# drop neighbourhoods outside the metro system 
MIQ1_db = MIQ1_db[!(MIQ1_db$neighbourhood %like% 
                      c('Cantalupa%','Noverasco%','Settimo Mila%','Bresso%',
                        "Chiaravalle%","Rozzano%",
                        "Vimodrone%","Cormano%") ),]

# in the analysis, we'll keep only neighbourhood_cleansed, so let's drop the other vars
MIQ1_db <- MIQ1_db[,!(names(MIQ1_db) %in% c("neighbourhood","neighbourhood_group_cleansed"))]

# and factor neighbourhood
MIQ1_db$neighbourhood_f = as.factor(MIQ1_db$neighbourhood_cleansed)
# and dummies
MIQ1_db <- dummy_cols(MIQ1_db, select_columns = "neighbourhood_cleansed", remove_first_dummy = TRUE) #remove option to avoid multicollinearity


```

### Property characteristics

#### Type of Room 
``` {r include = F, message = FALSE , warning = FALSE}
# Property characteristics
# Room type - Main variable 
length(which(is.na(MIQ1_db$room_type))) # no NAs
unique(MIQ1_db$room_type)

# Property type - more specific
length(which(is.na(MIQ1_db$property_type))) # no NAs
unique(MIQ1_db$property_type)
```

We would like to drop any type of accommodation that is not a private accomodation - i.e. drop Hotel room

``` {r include = T, message = FALSE , warning = FALSE}
# keep if property type is Apartment, House or Townhouse
MIQ1_db <- MIQ1_db[!(MIQ1_db$room_type %like% 'Hotel%'),]

# let's check in property_type - more detailed
MIQ1_db$property_type <- tolower(MIQ1_db$property_type)
MIQ1_db <- MIQ1_db[!(MIQ1_db$property_type %like% c('%hostel','%guesthouse','%hotel','%bed and breakfast', '%camper/rv%','boat')),]

# creat factor and dummies on room_type
MIQ1_db$room_type_f <- as.factor(MIQ1_db$room_type)

MIQ1_db <- MIQ1_db %>% mutate(variable = fct_recode(room_type_f,"Entire_prop" = "Entire home/apt",
     "Private_room"   = "Private room", "Shared_room" = "Shared room"))

MIQ1_db <- dummy_cols(MIQ1_db, select_columns = "room_type_f", remove_first_dummy = TRUE) #remove option to avoid multicollinearity


```


#### Guests capacity 

``` {r include = F, message = FALSE , warning = FALSE}
# Nr accepted people 
class(MIQ1_db$accommodates)
length(which(is.na(MIQ1_db$accommodates)))

summary(MIQ1_db$accommodates)

```

#### Size of the property
Lets create a categorical variable starting from the nr of bedrooms

``` {r include = T, message = FALSE , warning = FALSE}
# Now let's classify the apt size by the nr of bedrooms
summary(MIQ1_db$bedrooms) # few Nas, drop them
MIQ1_db<- MIQ1_db[!is.na(MIQ1_db$bedrooms),]

MIQ1_db$bedrooms_f <- NA  
MIQ1_db$bedrooms_f[MIQ1_db$bedrooms == 0 ] <- '0Broom'
MIQ1_db$bedrooms_f[MIQ1_db$bedrooms == 1 ] <- '1Broom'
MIQ1_db$bedrooms_f[MIQ1_db$bedrooms == 2 ] <- '2Broom'
MIQ1_db$bedrooms_f[MIQ1_db$bedrooms == 3 ] <- '3Broom'
MIQ1_db$bedrooms_f[MIQ1_db$bedrooms == 4 ] <- '4Broom'
MIQ1_db$bedrooms_f[MIQ1_db$bedrooms >= 5 ] <- '5+Broom'
MIQ1_db$bedrooms_f <- as.factor(MIQ1_db$bedrooms_f)

```

#### Bathrooms (nr and shared dummy) 

``` {r include = T, message = FALSE , warning = FALSE}

# Nr. Bathrooms
summary(MIQ1_db$bathrooms)
# 2 missings

# # replace with text when there is no info
# MIQ1_db$bathrooms[is.na(MIQ1_db$bathrooms)] <- substr(MIQ1_db$bathrooms_text[is.na(MIQ1_db$bathrooms)], 1, 2)
# 
# MIQ1_db$bathrooms[MIQ1_db$bathrooms == "Ha"] <- "0.5"
# 
# conditions <- substr(MIQ1_db$bathrooms,2,2) == "." & (MIQ1_db$bathrooms != "0.5") &
#                     !(is.na(MIQ1_db$bathrooms)) 
# 
# MIQ1_db$bathrooms[conditions == T] <- substr(MIQ1_db$bathrooms_text[conditions == T], 1, 3)
# 
# print('Final nr of NAs')
# length(which(is.na(MIQ1_db$bathrooms))) 

# finally, turn into numeric variable
MIQ1_db$bathrooms <- as.numeric(MIQ1_db$bathrooms)

MIQ1_db <- MIQ1_db[!is.na(MIQ1_db$bathrooms),]
# Categorical: no bathroom, one bathroom, >1 bathroom (as integers)
MIQ1_db$bathrooms_f <- NA
MIQ1_db$bathrooms_f[MIQ1_db$bathrooms == 0 ] <- '0'
MIQ1_db$bathrooms_f[MIQ1_db$bathrooms > 0 & MIQ1_db$bathrooms < 2 ] <- '1'
MIQ1_db$bathrooms_f[MIQ1_db$bathrooms >= 2] <- '2_over' 
MIQ1_db$bathrooms_f <- as.factor(MIQ1_db$bathrooms_f)
table(MIQ1_db$bathrooms_f)

# Dummy Shared Bath
MIQ1_db$d_sharebath <- 0
MIQ1_db$d_sharebath[MIQ1_db$bathrooms_text %like% c('%share%', '%Share%')] <- 1
MIQ1_db$d_sharebath[is.na(MIQ1_db$bathrooms)] <- NA
table(MIQ1_db$d_sharebath)


```

#### Amenities 

``` {r include = F, message = FALSE , warning = FALSE}

# code a function to extrac them all
extract_unique_amenities <- function(df, column_name) {
  # Remove brackets and quotes, split into a list, and convert to lowercase
  all_amenities <- tolower(unlist(strsplit(gsub("\\[|\\]|\"", "", df[[column_name]]), ", ")))
  
  # Get unique values
  unique_amenities <- unique(all_amenities)
  
  return(unique_amenities)
}

# make col lower capital
MIQ1_db$amenities <- tolower(MIQ1_db$amenities)

# Example usage
unique_amenities_db <- extract_unique_amenities(MIQ1_db, "amenities")
# print(unique_amenities_db) # more than 3.6k different amenities
```

Let's select some meaningful ones by key words, and create specific dummies. 

``` {r include = T, message = FALSE , warning = FALSE}
# Define amenities and corresponding keywords - already checked if meaningful in the list
amenities_list <- list(
  d_am_selfcheckin = c('%check%', '%check-in%', '%self%', '%check in%'),
  d_am_locker = c('%safe%', '%lock%'),
  d_am_housekeepingserv = c('%cleaning available%', '%housekeeping%'),
  d_am_fastwifi = c('%fast wifi%', '%internet%'),
  d_am_outdoor = c('%balcon%', '%view%', '%garden%', '%skyline%', '%patio%', '%loggia%', '%outdoor%'),
  d_am_petsallowed = c('%pets allowed%'),
  d_am_kitchen = c('%kitchen%'),
  d_am_essentials = c('%linen%', '%shampoo%', '%kit %')
)

# Loop through each amenity, create dummies
for (amenity in names(amenities_list)) {
  MIQ1_db[[amenity]] <- 0
  MIQ1_db[[amenity]] <- as.integer(
  Reduce('|', lapply(amenities_list[[amenity]], function(pattern) MIQ1_db$amenities %like% pattern))
)
  MIQ1_db[[amenity]] <- as.factor(MIQ1_db[[amenity]])
}

# Additional rules for exceptions
MIQ1_db$d_am_locker[MIQ1_db$amenities %like% "%baby safety gates%"] <- 0
MIQ1_db$d_am_outdoor[MIQ1_db$amenities %like% "%outdoor furniture%"] <- 0


# table(MIQ1_db$d_am_kitchen) # most bnbs have kitchens
```

## 1.4 Reviews 
``` {r include = F, message = FALSE , warning = FALSE}

cols <- names(MIQ1_db)[c(20:26,28:35)]

print("NAs by variable")
for (col in cols) {
  
  na_nr = sum(is.na(MIQ1_db[[col]]) )
  
  if (sum(is.na(MIQ1_db[[col]])) > 0) {
  
    print(col)
    print(na_nr)
    
  }
}

print(cols)
# keep max/min nights , nr reviews, availabilities (no NAs)
# drop score rating and review per month (too many NAs, ~20%)
summary(MIQ1_db$number_of_reviews)

```
# 2 Data Visualisation

## 2.1 Price - Dependent variable

``` {r include = T, message = FALSE , warning = FALSE}

summary(MIQ1_db$price_n)
quantile(MIQ1_db$price_n, probs = c(0.95, 0.96,0.99), na.rm = T) 
# 99% distribution at 1000
summary(MIQ1_db$price_ln)

p1 <- ggplot(MIQ1_db, aes(x = price_n)) +
  geom_histogram(aes(y = ..density..), bins = 50, fill = "cadetblue", color = "black", alpha = 0.6) +
  xlim(0,1000)+
    geom_density(color = "aquamarine4", size = .67) +
    labs(title = "Level scale", x = "", y = "Density")+
  theme_bw() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1, family = "Garamond", face = "bold"),
    axis.text.y = element_text(family = "Garamond", face = "bold"),
    axis.title.y = element_text(family = "Garamond"),
    plot.title = element_text(family = "Garamond"))

p2 <- ggplot(MIQ1_db, aes(x = price_ln)) +
  geom_histogram(aes(y = ..density..), bins = 40, fill = "hotpink4", color = "black", alpha = 0.6) +
  xlim(0,11.5)+
    geom_density(color = "magenta4", size = .67) +
    labs(title = "Log scale", x = "", y = "")+
  theme_bw() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1, family = "Garamond", face = "bold"),
    axis.text.y = element_text(family = "Garamond", face = "bold"),
    axis.title.y = element_text(family = "Garamond"),
    plot.title = element_text(family = "Garamond"))

plot_p <- ggarrange(p1,p2)

annotate_figure(plot_p, top = text_grob("USD Price distribution AirBnB, MIQ1", 
               color = "black", family = "Garamond", size = 14))
```
Log distribution looks well-behaved, go for log transformation. 

## 2.2 Factoral variables

### Room type

``` {r include = T, message = FALSE , warning = FALSE}

ggplot(MIQ1_db, aes(x= room_type, y= price_ln, fill = room_type)) + 
    geom_boxplot(alpha=0.5) +
  xlab('')+ ylab('USD log-price')+
  ggtitle('Room Type')+
  scale_fill_brewer(palette="BuPu")+ 
  theme_bw() +
  theme(
    legend.position="none",
    axis.text.x = element_text(family = "Garamond", face = "bold"),
    axis.text.y = element_text(family = "Garamond", face = "bold"),
    axis.title.y = element_text(family = "Garamond"),
    plot.title = element_text(family = "Garamond")) 
```    

#### Interaction between Room type and dummy Pets allowed

No meaningful results in this case

``` {r include = T, message = FALSE , warning = FALSE}

MIQ1_db %>% tabyl(bathrooms, d_sharebath) # there's variation across categories

ggplot(MIQ1_db, aes(x= d_am_petsallowed, y= price_ln, fill = as.factor(d_am_petsallowed))) + 
    geom_boxplot(alpha=0.5) +
  xlab('')+ ylab('USD log-price')+
  labs(fill = "Pets allowed")+
  scale_fill_brewer(palette="BuPu")+ 
  theme_bw() +
  theme(
    legend.position="bottom", legend.title = element_text(family = "Garamond"),
    axis.text.x = element_text(family = "Garamond", face = "bold"),
    axis.text.y = element_text(family = "Garamond", face = "bold"),
    axis.title.y = element_text(family = "Garamond"),
    axis.title.x = element_text(family = "Garamond"),
    plot.title = element_text(family = "Garamond")) 

# no difference    

```

### Apt size (Nr. bedrooms)

``` {r include = T, message = FALSE , warning = FALSE}

b1<- ggplot(MIQ1_db, aes(x= as.factor(bedrooms), y= price_ln, fill = as.factor(bedrooms))) + 
    geom_boxplot(alpha=0.5) +
  xlab('')+ ylab('USD log-price')+
  ggtitle('Nr. Bedrooms')+
  scale_fill_brewer(palette="BuPu")+ 
  theme_bw() +
  theme(
    legend.position="none",
    axis.text.x = element_text(family = "Garamond", face = "bold"),
    axis.text.y = element_text(family = "Garamond", face = "bold"),
    axis.title.y = element_text(family = "Garamond"),
    plot.title = element_text(family = "Garamond")) 

b2<- ggplot(MIQ1_db, aes(x= as.factor(bedrooms_f), y= price_ln, fill = as.factor(bedrooms_f))) + 
    geom_boxplot(alpha=0.5) +
  xlab('')+ ylab('')+
  ggtitle('Categorical (Apt size)')+
  scale_fill_brewer(palette="BuPu")+ 
  theme_bw() +
  theme(
    legend.position="none",
    axis.text.x = element_text(family = "Garamond", face = "bold", angle = 90),
    axis.text.y = element_text(family = "Garamond", face = "bold"),
    axis.title.y = element_text(family = "Garamond"),
    plot.title = element_text(family = "Garamond")) 

plot_aptsize <- ggarrange(b1,b2)

annotate_figure(plot_aptsize , top = text_grob("Flat size numeric vs categorical, MIQ1", color = "black", family = "Garamond", size = 14))

```    

Keep categorical - create dummies

``` {r include = F, message = FALSE , warning = FALSE}

MIQ1_db <- dummy_cols(MIQ1_db, select_columns = "bedrooms_f", remove_first_dummy = TRUE) #remove option to avoid multicollinearity


```

Also, let's check the correlation with the **accommodates** variable:

``` {r include = T, message = FALSE , warning = FALSE}
cor(MIQ1_db$bedrooms, MIQ1_db$accommodates , use = 'complete.obs')
```
High, but no multicollinearity. Consider to include them first separately then together.  

### Correlation tabs wrt price (factors)

Among dummies: Self check-in and locker are highly correlated
*Price correlation: no amenity seems to be extremely meaningful. Having a kitchen shows highest coeff, essentials and locker the lowest* 

``` {r include = T, message = FALSE , warning = FALSE}

dummy_vars <- MIQ1_db %>%
  select(starts_with("d_am_"), starts_with("bedrooms_f"), starts_with('room_type_f'),price_ln) %>%
  mutate_all(~ as.numeric(.))

# Compute correlation matrix
cor_matrix <- cor(dummy_vars, use = "pairwise.complete.obs")

# and plot correlation matrix
ggcorrplot(cor_matrix, 
           method = "circle", 
           type = "lower", 
           lab = TRUE, 
           title = "Correlation Matrix of Dummy Amenities")+
  theme(
    legend.title = element_text(family = "Garamond"),
    axis.text.x = element_text(family = "Garamond", face = "bold"),
    axis.text.y = element_text(family = "Garamond", face = "bold"),
    plot.title = element_text(family = "Garamond")) 

```
Selection criteria: at least ~ .05 coefficient.
Amenities: keep them all, might be relevant for other samples

## 2.3 Numerical variables - functional form

### Accommodates nr 

We include it as categorical, with linear fit

``` {r include = T, message = FALSE , warning = FALSE}
ggplot(MIQ1_db,aes(x= accommodates , y = price_ln)) + 
  geom_point(color='dodgerblue3', alpha = 0.8)+  # Scatter plot for points
  stat_smooth(method='lm', formula='y ~ poly(x, 1)', color='firebrick4', size = .75) + 
  labs(title="Accomodates functional form", x='', y='USD Log Price')+
  theme_bw() +
  theme(
    axis.text.x = element_text(family = "Garamond", face = "bold"),
    axis.text.y = element_text(family = "Garamond", face = "bold"),
    axis.title.y = element_text(family = "Garamond"),
    axis.title.x = element_text(family = "Garamond"),
    plot.title = element_text(family = "Garamond")) 



```
keep linear 

### Correlation tab numerical variables with price

Select variables we want to include in the correlation tab

``` {r include = T, message = FALSE , warning = FALSE}


numericals <- c("host_resptime_n", "host_response_rate", 'bedrooms', "accommodates","review_scores_rating","number_of_reviews","minimum_nights",'maximum_nights',"beds", 'availability_30','availability_60','availability_90','availability_365')

num_vars <- MIQ1_db %>%
  select(sort(numericals), price_ln) %>%
  mutate_all(~ as.numeric(.))

# Compute correlation matrix
cor_matrix <- cor(num_vars, use = "pairwise.complete.obs")

# and plot correlation matrix
ggcorrplot(cor_matrix, 
           method = "circle", 
           type = "lower", 
           lab = TRUE, 
           title = "Correlation Matrix of Numerical variables")+
  theme(
    legend.title = element_text(family = "Garamond"),
    axis.text.x = element_text(family = "Garamond", face = "bold"),
    axis.text.y = element_text(family = "Garamond", face = "bold"),
    plot.title = element_text(family = "Garamond")) 


```
Selection criteria: at least ~ .05 coefficient. 
Drop host_response rate. We use accommodates (higher correlation than beds, drop it), plus bedrooms (as categorical), availability_30 (highest corr)


# 3. save cleaned database
``` {r include = T, message = FALSE , warning = FALSE}
write_rds(MIQ1_db, 'MIQ1_db_clean.rds')
```
